Democratizing Secure Two-Party Computation

### 2017-10-15 OaklandSubmission/intro.tex

In this work, we develop and implement our framework \tool \nc{I still like EasyPC :)} \divya{I agree that \tool is bad. What would be the full form for EasyPC? Shouldn't it be EasySC?} for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level \divya{C-like} program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions in more detail.}

@@

\subsection{\tool: Overview and Contributions} 
\label{sec:contrib}
%Write high level overview of programming language and tool.. \divya{have some preamble}
\divya{I can add paragraph headings..}

@@

\textbf{Type system.} We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.
\nc{Shall we have paragraph heads or something to outline the different contributions? Above feels like one big story.}

>>>>

In this work, we develop and implement our framework \tool \nc{I still like EasyPC :)} \divya{I agree that \tool is bad. What would be the full form for EasyPC? Shouldn't it be EasySC?} for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level \divya{C-like} program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{eval}). Below, we will  give an overview of \tool and describe our contributions in more detail.

@@

\subsection{\tool: Overview and Contributions} 
\label{sec:contrib}
%Write high level overview of programming language and tool.. \divya{have some preamble}

@@

\textbf{Type system.} We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.

### 2017-10-15 OaklandSubmission/pipe.tex

\section{Pipelining}
\label{sec:pipe}
\nc{Started high level description. Can go deeper and correct notation as we proceed.}
We now describe our technique of ``pipelining'' that allows us to compile and execute large programs that would otherwise have not fitted in memory (due to the large size of the circuit generated by ABY). We do this securely in a manner such that the underlying backend (such as ABY in this case) does not have to modified in anyway and hence our technique is also compatible with any backend. In more detail, let $P$ be a program in our source language that gets compiled to $P'$ in our target language. In many cases, the ABY circuit generated for $P'$ is very large and cannot fit in memory (in fact, there is an upper limit of $2^{32}$ for the circuit size in ABY and for many natural programs, this upper limit is easily crossed). Without pipelining, we would be unable to compile and execute such a program $P$. In order to overcome this size limit, we do the following: we split the program $P$ into a sequence of smaller programs $Q_1||Q_2||\cdots||Q_k$ (that will be appropriately defined). We compile and execute each $Q_i$ separately, feeding the outputs of one program as state information to the next program. Of course, we have to be careful how we do this so as to not compromise the security of the protocol. More details follow.

Let $P$ be a program that takes as (secret) inputs $x$ and $y$ and produces output $z$ to both parties. Let $P_1||P_2||\cdots||P_k$ be a sequence of programs defined such that the following holds. Define $s_0 = \bot$ (the public empty state). For all $1\leq i\leq k-1$, $P_i$ takes as input $x, y$ and $s_{i-1}$ to produce state information $s_i$. Finally, $P_k$ takes as input $x,y$ and $s_{k-1}$ to produce output $z$. Every program $P_i$ ($1\leq i\leq k$) will be required to be ``sufficiently'' small (as described later) and this will enable our pipelining technique. It is easy to see that any program $P$ can be decomposed as illustrated above into such $P_1||P_2||\cdots||P_k$. Now, if one were to compile $P_i$ into $P'_i$, and execute $P'_i$, the parties can execute $P'_1||P'_2||\cdots||P'_k$ sequentially to obtain $s_1,\cdots,s_{k-1},$ and finally output $z$. However, doing so would enable the parties to learn $s_i$ (for all $1\leq i\leq k-1$), which would completely break the security of the protocol.

To overcome this problem, we define a sequence of new programs $Q_i$ ($1\leq i\leq k$) as follows. Once again, define $s_0 = \bot$. Let all $s_i$ be values in some additive ring $(\mathbb{Z},+)$ (in the ABY implementation this ring would simply be the additive ring $(\mathbb{Z}_{2^{32}},+)$ i.e., the additive ring of integers modulo $2^{32}$). This is without loss of generality true (we will also for simplicity assume that each $s_i$ is a single element in the ring, but this restriction can also be easily removed). Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from the same ring $(\mathbb{Z},+)$ by Party A. Let $Q_1$ be the program that takes as input $x,y, r_1$ (and empty state $s_0$), runs $P_1$ (as defined above) to get $s_1$ and then produces output $o_1 = s_1 + r_1$ {\em only to} Party B\footnote{While the description of our protocol here assumes that the underlying backend supports only one party receiving output, this is only a simplifying assumption, and we can easily modify our protocol in the case where both parties must receive the same output. To do so, we let $Q_1$ output $o_1 = s_1+r_1+t_1$ (where $t_1$ is random and chosen by Party B) and have both parties learn this. We can then appropriately modify the remaining steps as well.}. The output of $Q_1$ for Party A is defined to be $r_1$. Now, every $Q_i$ ($2\leq i\leq k-1$) takes as input $x,y,r_{i-1},o_{i-1},r_i$, runs $P_i$ on inputs $x,y$ and state $o_{i-1}-r_{i-1}$ to get $s_i$ (where $-$ denotes subtraction in the ring $(\mathbb{Z},+)$) and then produces $s_i+r_i$ as output only to Party B. Again, Party A's output for $P_i$ is defined to be $r_i$. $Q_k$ takes as input $x,y,r_{k-1},o_{k-1}$, runs $P_k$ on inputs $x,y$ and state $o_{k-1}-r_{k-1}$ and outputs $z$ to both parties.

>>>>

\section{Pipelining}
\label{sec:pipe}
\nc{Started high level description. Can go deeper and correct notation as we proceed.}
We now describe our technique of ``pipelining'' that allows us to compile and execute large programs that would otherwise have not fit in memory (due to the large size of the circuit generated by ABY). We do this securely in a manner such that the underlying backend (such as ABY in this case) does not have to modified in anyway and hence our technique is also compatible with any backend. In more detail, let $P$ be a program in our source language that gets compiled to $P'$ in our target language. In many cases, the ABY circuit generated for $P'$ is very large and cannot fit in memory (in fact, there is an upper limit of $2^{32}$ for the circuit size in ABY and for many natural programs, this upper limit is easily crossed). Without pipelining, we would be unable to compile and execute such a program $P$. In order to overcome this size limit, we do the following: we split the program $P$ into a sequence of smaller programs $Q_1||Q_2||\cdots||Q_k$ (that will be appropriately defined). We compile and execute each $Q_i$ separately, feeding the outputs of one program as state information to the next program. Of course, we have to be careful how we do this so as to not compromise the security of the protocol. More details follow.

Let $P$ be a program that takes as (secret) inputs $x$ and $y$ and produces output $z$ to both parties. Let $P_1||P_2||\cdots||P_k$ be a sequence of programs defined such that the following holds. Define $s_0 = \bot$ (the public empty state). For all $1\leq i\leq k-1$, $P_i$ takes as input $x, y$ and $s_{i-1}$ to produce state information $s_i$. Finally, $P_k$ takes as input $x,y$ and $s_{k-1}$ to produce output $z$. Every program $P_i$ ($1\leq i\leq k$) will be required to be ``sufficiently'' small (as described later) and this will enable our pipelining technique. It is easy to see that any program $P$ can be decomposed as illustrated above into such $P_1||P_2||\cdots||P_k$. Now, if one were to compile $P_i$ into $P'_i$, and execute $P'_i$, the parties can execute $P'_1||P'_2||\cdots||P'_k$ sequentially to obtain $s_1,\cdots,s_{k-1},$ and finally output $z$. At the $i^{\textrm{\tiny{th}}}$ step, the parties would only need to store information proportional to $x,y,s_i$ and $P'_i$ (which will all be much smaller than $P'$). However, if we were to execute the programs as outlined above, it would enable the parties to learn $s_i$ (for all $1\leq i\leq k-1$), which would completely break the security of the protocol.

To overcome this problem, we define a sequence of new programs $Q_i$ ($1\leq i\leq k$) as follows. Once again, define $s_0 = \bot$. Let all $s_i$ be values in some additive ring $(\mathbb{Z},+)$ (in the ABY implementation this ring would simply be the additive ring $(\mathbb{Z}_{2^{32}},+)$ i.e., the additive ring of integers modulo $2^{32}$). This is without loss of generality true (we will also for simplicity assume that each $s_i$ is a single element in the ring, but this restriction can also be easily removed). Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from the same ring $(\mathbb{Z},+)$ by Party A (in our implementation, all $r_i$ values can be generated using a pseudorandom function $F$). Let $Q_1$ be the program that takes as input $x,y, r_1$ (and empty state $s_0$), runs $P_1$ (as defined above) to get $s_1$ and then produces output $o_1 = s_1 + r_1$ {\em only to} Party B\footnote{While the description of our protocol here assumes that the underlying backend supports only one party receiving output, this is only a simplifying assumption, and we can easily modify our protocol in the case where both parties must receive the same output. To do so, we let $Q_1$ output $o_1 = s_1+r_1+t_1$ (where $t_1$ is random and chosen by Party B) and have both parties learn this. We can then appropriately modify the remaining steps as well.}. The output of $Q_1$ for Party A in Step 1 is defined to be $r_1$. Now, every $Q_i$ ($2\leq i\leq k-1$) takes as input $x,y,r_{i-1},o_{i-1},r_i$, runs $P_i$ on inputs $x,y$ and state $o_{i-1}-r_{i-1}$ to get $s_i$ (where $-$ denotes subtraction in the ring $(\mathbb{Z},+)$) and then produces $s_i+r_i$ as output only to Party B. Again, Party A's output for $P_i$ is defined to be $r_i$. $Q_k$ takes as input $x,y,r_{k-1},o_{k-1}$, runs $P_k$ on inputs $x,y$ and state $o_{k-1}-r_{k-1}$ and outputs $z$ to both parties.
